---
output:
  bookdown::pdf_book:
    keep_tex: yes
  bookdown::gitbook:
    lib_dir: "book_assets"
documentclass: book
---

# Land_use

```{r, include=TRUE}
library(tidyverse)
library(sp)
library(osmdata)
library(dodgr)
#library (osmplotr)
library (magrittr)
library(geodist)
library(spocc)
library(sf)
library(ggthemes)
```

## Land use
These are the points or polygons where growth happens. There is some suitability for growth that determinines the growth rate in that patch.

1) Provide a bounding box (best), place name (good), or polygon (buggy) to download OSM
2) Specify land use type with OSM tag codes
3) Snap species abundance data to chosen nodes. 
4) Out comes XY coordinates with abundance and suitability assigned. 

### Specify extent 
```{r}
bb <- osmdata::getbb ("Montréal canada") # montreal canada

#Montreal place name + more surrounding area. This was as largest as I could download within API limits. 
my_bbox <-  bb #c(-74.155338,45.344097,  -73.284492, 45.727531)
```

### Choose land use type
#### Open Street Map TAGS
Pull polygons from OVERPASS API.
These downloads use a "KEY" and "VALUE" system of identifying datasets (see https://wiki.openstreetmap.org/wiki/Tags). 

Find tags here:
https://taginfo.openstreetmap.org 

#### Downloading complete OSM datasets
This version dowloads a long-form version of the data in the form of 8-10 individual dataframes
```{r, eval=FALSE}
not_restaurants <- opq(bbox = c(-74.155338,45.344097,  -73.284492, 45.727531), timeout = 900) %>% # Greater Montreal
    add_osm_feature(key = "amenity", value = "!restaurant") %>%
    osmdata_sc() #This specifies downloading an SC file
not_restaurants
```


#### Downloading shape files from OSM

```{r}
poly_areas <- function(sf_object, landuse_type){
if(length(sf_object$osm_multipolygons) > 0){
  poly_area <- st_area(sf_object$osm_polygons)
multi_poly_area <- st_area(sf_object$osm_multipolygons)
log_area1 <- as.data.frame(as.numeric(log(poly_area)))
log_area2 <- as.data.frame(as.numeric(log(multi_poly_area)))
names(log_area1) <- "log_area"
names(log_area2) <- "log_area"
log_area <- rbind(log_area1, log_area2) 
} else {
  poly_area <- st_area(sf_object$osm_polygons)
log_area <- as.data.frame(as.numeric(log(poly_area)))
names(log_area) <- "log_area"
}

area_df <- cbind(log_area, rep(landuse_type, length(log_area[,1])))
names(area_df)[2] <- "type"
area_df <- na.omit(area_df)
return(area_df)
}
```

This version downloads a shapefile of the points, lines, polygons, or multipolygons of interest.
```{r}
name <- "montreal"
land_use <- function(name, pop_size){
full_name <- paste(name, "canada", sep=" ")
try(my_bbox <- osmdata::getbb (full_name)) # montreal canada

dat1 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'park') %>%
    osmdata_sf ()
dat2 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'garden') %>%
    osmdata_sf ()
dat3 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'nature_reserve') %>%
    osmdata_sf ()
dat4 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'dog_park') %>%
    osmdata_sf ()
dat5 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'common') %>%
    osmdata_sf ()
dat6 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'pitch') %>%
    osmdata_sf ()
dat7 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'horse_riding') %>%
    osmdata_sf ()
naturals <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'natural', value = 'wood') %>%
    osmdata_sf ()
greens <- c (dat1, dat2, dat3, dat4, dat5, dat6, dat7, naturals)


buildings <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'building') %>%
    osmdata_sf ()

roads <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'landuse', value = 'residential') %>%
    osmdata_sf ()

agriculture <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'landuse', value = 'farmland') %>%
    osmdata_sf()

greens_df <- poly_areas(greens, "green space")
buildings_df <- poly_areas(buildings, "buildings")
paved_df <- poly_areas(roads, "paved")
ag_df <- poly_areas(agriculture, "agriculture")
all_types <- rbind(greens_df, buildings_df, paved_df, ag_df)
all_types2 <- cbind(all_types, log(pop_size))
names(all_types2)[3] <- "pop_size"
return(all_types2)
}

```

```{r}
name <- "montreal"
all_green_space <- function(name, pop_size){
full_name <- paste(name, "canada", sep=" ")
try(my_bbox <- osmdata::getbb (full_name)) # montreal canada

dat1 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'park') %>%
    osmdata_sf ()
#dat2 <- opq(bbox = my_bbox, timeout = 900) %>%
#    add_osm_feature(key = 'leisure', value = 'garden') %>%
#    osmdata_sf ()
dat3 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'nature_reserve') %>%
    osmdata_sf ()
dat4 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'dog_park') %>%
    osmdata_sf ()
dat5 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'common') %>%
    osmdata_sf ()
dat6 <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'leisure', value = 'pitch') %>%
    osmdata_sf ()
#dat7 <- opq(bbox = my_bbox, timeout = 900) %>%
#    add_osm_feature(key = 'leisure', value = 'horse_riding') %>%
#    osmdata_sf ()
naturals <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'natural', value = 'wood') %>%
    osmdata_sf ()
greens <- c (dat1, dat2, dat4, dat5, dat6, naturals)

greens_df <- poly_areas(greens, "green space")
if(nrow(greens_df) > 0){
all_types <- rbind(greens_df) #, buildings_df, paved_df, ag_df
all_types2 <- cbind(all_types, log(pop_size))
names(all_types2)[3] <- "pop_size"
return(all_types2)
}
}

```

```{r}
name <- "Moffet"
pop_size  <- 187
all_agriculture <- function(name, pop_size){
full_name <- paste(name, "canada", sep=" ")
try(my_bbox <- osmdata::getbb (full_name)) # montreal canada


agriculture <- opq(bbox = my_bbox, timeout = 900) %>%
    add_osm_feature(key = 'landuse', value = 'farmland') %>%
    osmdata_sf()
#gardens <- opq(bbox = my_bbox, timeout = 900) %>%
    #add_osm_feature(key = 'leisure', value = 'garden') %>%
    #osmdata_sf ()
#ag <- c(agriculture, gardens)

#ag_df <- poly_areas(ag, "green space")
#buildings_df <- poly_areas(buildings, "buildings")
#paved_df <- poly_areas(roads, "paved")

ag_df <- poly_areas(agriculture, "agriculture")
if(nrow(ag_df) > 0){
all_types <- rbind(ag_df) #, buildings_df, paved_df, ag_df
all_types2 <- cbind(all_types, log(pop_size))
names(all_types2)[3] <- "pop_size"
return(all_types2)
} 
}

```

```{r}
library(cancensus)
city_list <- list_census_regions("CA16") %>%
filter(level == "CSD") %>% 
select(c(name, pop))
plot(log(city_list$pop), xlab="rank", ylab="size = log(city population)")
plot(city_list$pop, type="l", xlab="rank", ylab="size = city population")
city_list[2000,]
```

```{r}
full_name <- paste(city_list[2000,1], "canada", sep=" ")

try(my_bbox <- osmdata::getbb (full_name) ) # montreal canada)

```



```{r}
length.out <- 1000

#all_types <- all_green_space(city_list[1,1],city_list[1,2])
#sample(length(city_list$pop), length.out)
for(i in 4467:5000){
try(all_types <- rbind(all_types, all_green_space(city_list[i,1],city_list[i,2])))
print(c(i,length(levels(as.factor(all_types[,3])))))
}
length(all_types[,1])

```

```{r}
all_types[which(is.infinite(all_types[,1]) == TRUE),] <- NA
all_types[which(is.nan(all_types[,1]) == TRUE),] <- NA
all_types[which(all_types[,1] < 0),] <- NA
all_types[which(is.infinite(all_types[,3]) == TRUE),] <- 0
all_types[which(is.nan(all_types[,3]) == TRUE),] <- NA
all_types_o <- na.omit(all_types) 

base_10 <- all_types_o
base_10[,3] <- log10(exp(all_types_o[,3]))
base_10[,1] <- log10(exp(all_types_o[,1]))
 
```


```{r}
city <- base_10[which(base_10[,2]== "green space"),] #there is a filter here. may need to adjust or remove
city[which(is.infinite(city[,3]) == TRUE),] <- 0
plot(y=city$log_area , x=city$pop_size, ylim=c(0,10),  col=adjustcolor("cornflowerblue", alpha=0.009))
abline(lm(log_area~pop_size, data=city))
text(x=10, y=25,label=round(lm(log_area~pop_size, data=city)$coef[2], digits = 2), adj=0, col=adjustcolor("cornflowerblue", alpha=1))


ggplot(data=base_10, aes(y = log_area, x=pop_size)) + geom_point(fill="red", alpha=0.005) + xlim(0,8) + theme_tufte()
```

```{r}
sums <- all_types_o %>%   
  group_by(pop_size) %>%
  summarise(count = sum(exp(log_area)))


ggplot(data=sums, aes(y=log(count), x=pop_size)) + geom_point( alpha=0.4) + xlim(0,22) + theme_tufte()

means <- all_types_o %>%   
  group_by(pop_size) %>%
  summarise(count = mean(exp(log_area)))


ggplot(data=means, aes(y=log10(count), x=pop_size)) + geom_point( alpha=0.4) + xlim(0,22) + theme_tufte()

```


```{r}
save(all_types_o, file="green_space_scaling.Rdata")
```


```{r}
#all_types_o_front <- all_types_o
load("/Users/Ty/Desktop/GitHub/OSM_SUS/all_types_o.Rdata")
all_types <- all_types_o
```


```{r}
all_types_o %>% filter(pop_size < 11 & pop_size > 10) %>% ggplot( aes(log_area)) + geom_density(fill="red")

ggplot(data=all_types_o, aes(log_area)) + geom_density(fill="red", alpha=0.4) + xlim(0,22) + theme_tufte()

```



plot shapefile
```{r}

sp::plot(greens$osm_polygons[1], border="green", fill="green")
sp::plot(agriculture$osm_polygons[1], border="red", fill="red")
```




### Format data for passing to metapopulation model
Need the polygones as XY coordinates or node IDs









```{r}
sidewalk <- opq(bbox = "montreal canada", timeout = 900) %>% 
  add_osm_feature(key = "sidewalk") %>% 
  osmdata_sf()
```
```{r}
sp::plot(sidewalk$osm_polygons)
```

